fdcoexist

### 2018-10-05 meta_simulations.Rmd
:bug: :boom: Very messy document to clean

# Competition + Dispersion coefficients
B = 2e-4 # Scalar for intraspecific competition
A = B	 # Alpha scalar
d = 0.05 # Dispersal percentage

@@

    apply(all_facets, 1, function(given_row) {
        multigen(traits = all_cor[[given_row[["cor_level"]]]],
                 trait_weights = trait_scenarios[[given_row[["scenario"]]]],
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = all_compet[[given_row[["compet_status"]]]][["A"]],
                 B = all_compet[[given_row[["compet_status"]]]][["B"]],
                 d = d,
                 k = given_k,
                 width = all_env[[given_row[["env_width"]]]]) %>%
            landscape_df(all_cor[[given_row[["cor_level"]]]],
                         trait_scenarios[[given_row[["scenario"]]]],
                         time = 150) %>%
            inner_join(all_cor[[given_row[["cor_level"]]]] %>%
                           as.data.frame() %>%
                           rownames_to_column("species"),
                       by = "species") %>%
            group_by(patch) %>%
            mutate(rel_abund = N/sum(N)) %>%
            ungroup() %>%
            mutate(compet_status = given_row[["compet_status"]],
                   env_width     = given_row[["env_width"]],
                   cor_level     = given_row[["cor_level"]],
                   scenario      = given_row[["scenario"]],
                   seed_number = seed_number) %>%
            select(seed_number, compet_status, env_width, cor_level, scenario,
                   everything())
    }) %>%
        bind_rows() %>%
        filter(N != 0) %>%  # Take out absent species
        mutate_at(vars(contains("trait")), funs(cwm = rel_abund * .)) %>%
        mutate(scenario = fct_relevel(scenario, names(trait_scenarios)),
               patch_optim = as.numeric(gsub("patches", "", patch))) %>%
        group_by(seed_number, compet_status, env_width, cor_level, scenario,
                 patch) %>%
        summarise(trait1_cwm  = sum(trait1_cwm),
                  trait2_cwm  = sum(trait2_cwm),
                  trait3_cwm  = sum(trait3_cwm),
                  trait1_var  = var(trait1),
                  trait2_var  = var(trait2),
                  trait3_var  = var(trait3),
                  patch_optim = unique(patch_optim))
}
# Generate traits --------------------------------------------------------------
trait_seed = 5
# Make traits with different correlations
set.seed(trait_seed)
uncor_traits = generate_cor_traits(n_patches, n_species, n_traits - 1,
                                   cor_coef = 0)
set.seed(trait_seed)
low_cor_traits = generate_cor_traits(n_patches, n_species, n_traits - 1,
                                     cor_coef = 0.3)

@@

    meta_simul(x, given_k = low_k)
}, .progress = TRUE)
tictoc::toc()

@@

>>>>

# Competition + Dispersion coefficients
B = 2e-4 # Scalar for intraspecific competition
A = 2e-4 # Alpha scalar
d = 0.05 # Dispersal percentage

@@

meta_simul_patch = function(seed_number, given_k = k, given_A = A) {
    set.seed(seed_number)
    uncor_traits = generate_cor_traits(n_patches, n_species, n_traits - 1,
                                       cor_coef = 0)

    all_cor = list(uncor    = uncor_traits)

    all_simuls = apply(all_facets, 1, function(given_row) {
        multigen(traits = all_cor[[given_row[["cor_level"]]]],
                 trait_weights = trait_scenarios[[given_row[["scenario"]]]],
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = all_compet[[given_row[["compet_status"]]]][["A"]],
                 B = all_compet[[given_row[["compet_status"]]]][["B"]],
                 d = d,
                 k = given_k,
                 width = all_env[[given_row[["env_width"]]]])
    #     %>%
    #         landscape_df(all_cor[[given_row[["cor_level"]]]],
    #                      trait_scenarios[[given_row[["scenario"]]]],
    #                      time = 150) %>%
    #         inner_join(all_cor[[given_row[["cor_level"]]]] %>%
    #                        as.data.frame() %>%
    #                        rownames_to_column("species"),
    #                    by = "species") %>%
    #         group_by(patch) %>%
    #         mutate(rel_abund = N/sum(N)) %>%
    #         ungroup() %>%
    #         mutate(compet_status = given_row[["compet_status"]],
    #                env_width     = given_row[["env_width"]],
    #                cor_level     = given_row[["cor_level"]],
    #                scenario      = given_row[["scenario"]],
    #                seed_number = seed_number) %>%
    #         select(seed_number, compet_status, env_width, cor_level, scenario,
    #                everything())
    })
    # %>%
    #     bind_rows() %>%
    #     filter(N != 0) %>%  # Take out absent species
    #     mutate_at(vars(contains("trait")), funs(cwm = rel_abund * .)) %>%
    #     mutate(scenario = fct_relevel(scenario, names(trait_scenarios)),
    #            patch_optim = as.numeric(gsub("patches", "", patch))) %>%
    #     group_by(seed_number, compet_status, env_width, cor_level, scenario,
    #              patch) %>%
    #     summarise(trait1_cwm  = sum(trait1_cwm),
    #               trait2_cwm  = sum(trait2_cwm),
    #               trait3_cwm  = sum(trait3_cwm),
    #               trait1_var  = var(trait1),
    #               trait2_var  = var(trait2),
    #               trait3_var  = var(trait3),
    #               patch_optim = unique(patch_optim))

    list(simul = all_simuls, trait = uncor_traits)
}
# Generate traits --------------------------------------------------------------
trait_seed = 5
# Make traits with different correlations
set.seed(trait_seed)
uncor_traits = generate_cor_traits(n_patches, n_species, n_traits - 1,
                                   cor_coef = 0)
set.seed(trait_seed)
low_cor_traits = generate_cor_traits(n_patches, n_species, n_traits - 1,
                                     cor_coef = 0.3)

@@

    meta_simul2(x, given_k = low_k)
}, .progress = TRUE)
tictoc::toc()

@@

```{r looking_at_slopes}
list_A = 2*10^-(seq(4, 6))
list_k = 1 + c(0.05, 0.15, 0.25)

var_k_var_a_cwm = var_k_var_a %>%
    bind_rows() %>%
    ungroup() %>%
    nest(-k, -A, -seed_number, -scenario) %>%
    mutate(data = data %>%
               map(~.x %>%
                       gather("cwm_name", "cwm_value", ends_with("cwm")) %>%
                       group_by(cwm_name, add = TRUE) %>%
                       do(mod_cwm_env = lm(cwm_value ~ patch_optim, data = .)) %>%
                       ungroup() %>%
                       mutate(mod_glance = lapply(mod_cwm_env, broom::tidy)) %>%
                       unnest(mod_glance))) %>%
    unnest(data) %>%
    filter(cwm_name == "trait2_cwm")
# 
# var_k_var_a_var = var_k_var_a %>%
#     map(~.x %>%
#             select(-ends_with("cwm"))) %>%
#     bind_rows() %>%
#     gather("var_name", "var_value", ends_with("var")) %>%
#     filter(var_name == "trait2_var") %>%
#     select(k, A, seed_number, everything())
```

We want to follow the dynamics through time to understand the variation in Rsquare
```{r}
patch_k_run_char = paste0("N = ", total_runs, "; A = ", A, "; B = ", B, "; k = ",
                        k)

patch_k_simuls = future_map(seq(total_runs), function(x) {
    devtools::load_all()

    meta_simul_patch(x, )
}, .progress = TRUE)
tictoc::toc()

patch_k_simuls[[1]][[1]][[1]]$compo[15,,] %>%
    as.data.frame() %>%
    rownames_to_column("species") %>%
    gather("time", "N", -species) %>%
    group_by(time) %>%
    mutate(tot_abund = sum(N)) %>%
    ungroup() %>%
    mutate(rel_abund = N / tot_abund) %>%
    inner_join(patch_k_simuls[[1]]$trait %>%
                   as.data.frame() %>%
                   rownames_to_column("species"),
               by = "species") %>%
    mutate_at(vars(starts_with("trait")), funs(precwm = rel_abund * .)) %>%
    group_by(time) %>%
    summarise_at(vars(ends_with("cwm")), sum) %>%
    mutate(time = as.numeric(gsub("time", "", time))) %>%
    gather("cwm_name", "cwm_value", contains("precwm")) %>%
    ggplot(aes(time, cwm_value)) +
    geom_line() +
    facet_grid(cols = vars(cwm_name))
```
